Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-11-17 Ben_Manuscripts/structure_paper/response_to_reviewers.tex

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{xr}

\externaldocument[S-]{supporting_information}
\externaldocument[M-]{Final_Draft}

@@

	\item \begin{quote}
	\textit{As written, it is not clear if the authors are presenting this study as a validation of 
	GAFF and the present equilibration techniques, or whether this study is providing significant new
	physical insight into these lyotropic liquid crystals. The paper reads a bit more like the former,
	with a comprehensive discussion of the degree to which five scattering features expected in 
	experiments are predicted in simulations. However, at the same time, the authors make arguments
	including (1) pores are made from five columns of monomers, (2) that water is present in the "dry"
	structures, and (3) that a scattering feature comes from tail packing, not tilt: These observations
	*could* be new physical insight into lyotropic liquid crystal structure, but as presented seem more
	like hypotheses than conclusions:}

	%BJC: want to convery that we want to reproduce all of the experimental features as best as possible
	% using an out-of-the-box force field. That way we know we are approximating the chemical environment
	% as close to the experimental system as possible. The goal is to eventually test large numbers of 
	% monomers without the needing to dive into the excruciating detail shown here.

	\end{quote}

	\item \begin{quote}
    \textit{1. For the simulations performed here, the authors do make a strong case that 5 columns per
    core gets the best pore-to-pore spacing (Figure 5). However, insufficient time is accessed to see 
    whether the 4-, 5-, and 6-column initial conditions move towards or away from the expected pore 
    spacing over many-microseconds trajectories. That said, for the quenches performed here, 5-columns
    per core seems more plausible than 4.}
	\end{quote}

	Author reply: We agree with the reviewer that 5-columns per core is more plausible than 4 and that much
    longer simulations may provide further supporting evidence. However, there is very little motion on
    the hundreds of nanoseconds timescale which we simulated which suggests that we will not gain any 
    significant new insight by extending our simulations into the microsecond regime. It is not feasible 
    for us to carry out these simulations as it would consume our computational resources with little reward.
    %BJC: The following might apply:
    Some confusion may have been generated by agreement of the disordered basin 6 column-per-pore system
    with experimental pore spacing. As mentioned in the text, the vertical stacking distance between monomers
    in that system is far too large. The columns are `stretch' in the $z$-direction allowing the pores take
    up less space on the $xy$ plane and thus pack closer together.

	\item \begin{quote}    
    \textit{Is this significant physical insight? It is insight, but the
    authors do not make a compelling case for how 5 columns would change how we think about these crystals,
    or how it would impact membrane engineering (or more importantly, whether these 5-column structures
    assemble in the solution phase, or are only locally stable).}
    \end{quote}

    Author reply: We thank the reviewer for pushing us to provide more significant physical insight based
    on the number of monomers per column. The number of columns-per-pore influences the pore radius which
    is important for determining the limits of size-exclusion-based separations. It also tells use the 
    density of interacting sites within the pore which may play a role in small molecule transport. We have
    added the following text to the main document at the end of Section~\ref{M-section:mon_per_pore} on 
    page _:

    ``The number of columns per pore dictates the density of interaction sites within each pore and the 
    pore radius. A higher number of interaction sites will surely play a role in transport of molecules
    that have an affinity for the monomer head groups. 
    %We measured the pore radius as the average distance from the pore center to each head group COM. 
    The pore radius increases with the number of columns per pore (See Figure~\ref{S-fig:pore_radius}. 
    This radius is likely related to the size of the molecules which can be excluded by this type of 
    membrane. We may be able to control LLC membrane pore size by selecting monomers that are stable
    in configurations with more columns-per-pore."

### 2018-11-17 Ben_Manuscripts/structure_paper/Final_Draft.tex
Working on response to reviewers

@@

  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment
  because monomers in the simulated system stack further apart than those in the
  experimental system (Table~\ref{table:correlation_length}). We calculated
  $z$-direction pair distribution functions, $g(z)$, as described in
  Section~\ref{section:correlation_length}.  The resulting distributions are
  generally characterized by decaying oscillatory behavior where the average
  distance between peaks corresponds to the average distance between stacked
  monomer head groups (Figure~\ref{fig:correlation}).  We calculated this
  equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between monomers
  using Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked
  monomers is greater than experiment by 0.5--0.9 \AA~across all cases, with
  disordered basins at the high end of that range. This behavior is not
  surprising since GAFF models atoms as point charges and does not appropriately
  model the aromatic $\pi-\pi$ interactions, which would make it more
  energetically favorable for the monomers to stack closer together
  \cite{wang_development_2004}. It is also possible that the tails prevent
  close stacking of monomer head groups and we do not achieve the timescales
  necessary for them to rearrange into a necessarily more tightly packed
  configuration. To test this chain-packing hypotheses, we equilibrated the
  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
  into a more tightly packed configuration. Before annealing and in order to
  stabilize the hexagonal phase at 500 K, we placed harmonic restraints with
  force constants of 1000 kJ mol$^{-1}$ nm$^{-2}$ between head group COMs within
  each column as well as between head group COMs in adjacent columns. We saw no
  improvement in packing distance over our 300 K models (see further discussion
  in Section~\ref{section:slow_dynamics}).

  The system size, in the $z$-direction, does not significantly alter $g(z)$.
  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
  system may be necessary to fully capture the correlation function. We therefore
  equilibrated a sandwiched system with twice as many monomers per column so that
  the system size doubled in the $z$-direction. The correlation length increases
  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
  correlation functions are nearly identical and oscillatory behavior persists
  throughout $g(z)$ in both cases (See
  Figure \ref{S-fig:z_correlation_overlay}).

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{1D correlation functions of the center of masses of aromatic head
	  groups, $g(z)$, show decaying oscillatory behavior and have consistent
	  correlation lengths with experiment. We calculated the correlation length by
	  fitting a decaying exponential function
	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
	  correlation length is longer for ordered basin systems
	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
	  correlation length for (d) because there are no clear peaks. We assume that
	  this correlation length is less than the vertical distance between
	  monomers.}\label{fig:correlation}
  \end{figure}

@@

  An exact quantitative comparison between the intensity and FWHM of the
  experimental and simulated cross-sections of R-$\pi$ is not feasible for
  several reasons. Experimental peaks broaden due to effects that we can not
  easily simulate such as finite size crystalline domains and instrumental % reference needed
  resolution~\cite{girolami_x-ray_2016}. In our simulated XRD patterns, 
  the system size imposes limitations
  on the resolution, which makes it difficult to reliably fit peaks. This is
  especially problematic when comparing the FWHM of the $q_z$ cross-section of
  R-$\pi$, where the experimental FWHM (0.11 $\AA^{-1}$) is similar to the bin
  size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).  Additionally, we model each
  atom with a Gaussian sphere of electron density, which is a simplification.
  However, we can explore reasons for which differences in the simulation
  structure could change the peak shapes and intensities to be in better
  agreement with experiment.

@@

  Increasing thermal noise in the $z$-direction will reduce the intensity
  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increased the
  thermal noise of the simplified parallel displaced system in the $z$-direction by
  12\% and 27\%, we saw a 3 and 15-fold decrease in the maximum intensity of 
  R-$\pi$ respectively (Figure~\ref{fig:intensity_vs_zsigma}). Despite the decrease in 
  intensity, the 3 cross-sections have the same shape 
  (Figure~\ref{fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
  not consistent with experiment.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
  thermal noise in the $z$-direction; however, the $q_r$ cross-section profile does
  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
  background intensity, relative to systems with simulation levels of disorder (blue)
  by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor 
  of 15 when we increase $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  However, when we allowed monomer columns to move independently in the
  $z$-direction, the intensity of R-$\pi$ drops and the $q_r$ cross-section of
  the simulated diffraction patterns smooths out. We can demostrate this by
  creating a simplified sandwiched configuration (as described above), with
  varying amounts of statistical correlation between columns (see
  Figure~\ref{fig:column_displacement}). In the low independent motion limit, the
  COM of columns are situated at the same $z$-coordinate.  We allow increasing
  independence of columns by randomly shifting each column in the $z$-direction
  according to a uniform distribution bounded by (0, $f \times \mathit{d}$) where
  $f$ ranges between 0 and 1 and $d$ is the vertical distance between scatterers.
  When $f = 1$, the columns move independently and the $q_r$ cross-section
  smooths out completely (Figure~\ref{fig:sf_qy_sr100}). Any amount of dependence
  results in some presence of sharp peaks, though significantly attenuated at $f$
  nearer 1. The intensity of R-$\pi$ also decreases with increasing column
  independence. We see an 9-fold decrease in the intensity of R-$\pi$ when $f=1$
  versus when $f=0$ for our simplified model systems.

@@

  It therefore seems likely that the discrepancy between the shape and intensity of
  R-$\pi$ generated from our simulations versus experiment is primarily due to
  highly correlated columns in our highly symmetric initial configurations.
  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
  would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
  average all $z$-slices of the 3D correlation function. Contributions to
  $g(z)$ from head groups in other columns within the same pore, and with head
  groups in different pores would cancel out. However, when we include all 
  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
  $z$-slices within 2.1~\AA~of the center of the correlation function 
  (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
  behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
  reinforced by head groups in neighboring columns which is not expected
  in a system where columns act independently.

@@

  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a
  system with uncorrelated columns, we modified the disorder in both the $r$ and
  $\theta$ directions by multiplying their values by a factor of 0.5 and 2
  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
  with experiment, meaning the quenched configuration contains about the right
  amount of disorder on the $xy$ plane. However, the relatively low quality of
  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
  simulation might not be the best comparison to experiment and that some form of
  initial configuration dependence causes extra structure.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
	  FWHM of the $q_r$ cross-section of R-$\pi$. When we cut the amount of $r$ and
	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
	  we double the disorder (Noise factor = 2), the FWHM decreases by
	  51\%.}\label{fig:qy_fwhm}
  \end{figure}

@@

  The ether dihedrals become decorrelated on a reasonable timescale when we raise
  the system temperature. At 300 K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
  not cross the $x$-axis until $\sim$105 ns meaning that tails fully rotate on average about 
  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
  function plateau's near a value of -0.2 which indicates that the tails are starting in 
  an unfavorable configuration. We implemented distance restraints between the centers of 
  mass of monomer head groups to preserve the hexagonal phase, then raised the temperature 
  of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
  decorrelation of the ether dihedrals after $\sim$11 ns with a plateau at 0, 
  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
  the resultant configuration back down to 300 K over 200 ns to see if the increased rotational
  freedom might allow the system to relax into to a more tightly packed configuration.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  	\centering
  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.pdf}
  	\caption{300K}\label{fig:dihedrals_300K}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  	\centering
  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.pdf} % Run : torsions.py -t tethered_columns.xtc -g tethered_columns.gro (the appropriate dihedral is the default)
  	\caption{500K}\label{fig:dihedrals_500K}
  \end{subfigure}
  \caption{The outer tail ether dihedrals become decorrelated on a reasonable
  timescale when we raise the system temperature. (a) The dihedrals do not
  become decorrelated for ca. 100 ns when the system is equilibrated at 300 K.
  (b) The ether dihedrals become decorrelated after 11 ns when the temperature
  of the system is increased to 500 K.}\label{fig:dihedrals}
  \end{figure}

>>>>

  %BJC: added.
  The number of columns per pore dictates the density of interaction sites within
  each pore and the pore radius. A higher number of interaction sites will 
  surely play a role in transport of molecules that have an affinity for the monomer
  head groups. 
  %We measured the pore radius as the average distance from the pore
  %center to each head group COM. 
  The pore radius increases with the number of 
  columns per pore (See Figure~\ref{S-fig:pore_radius}. This radius is likely 
  related to the size of the molecules which can be excluded by this type of 
  membrane. We may be able to control LLC membrane pore size by selecting monomers
  that are stable in configurations with more columns-per-pore.

@@

  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment
  because monomers in the simulated system stack further apart than those in the
  experimental system (Table~\ref{table:correlation_length}). We calculated
  $z$-direction pair distribution functions, $g(z)$, as described in
  Section~\ref{section:correlation_length}. The resulting distributions are
  generally characterized by decaying oscillatory behavior where the average
  distance between peaks corresponds to the average distance between stacked
  monomer head groups (Figure~\ref{S-fig:correlation}). We calculated this
  equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between monomers
  using Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked
  monomers is greater than experiment by 0.5--0.9 \AA~across all cases, with
  disordered basins at the high end of that range. This behavior is not
  surprising since GAFF models atoms as point charges and does not appropriately
  model the aromatic $\pi-\pi$ interactions, which would make it more
  energetically favorable for the monomers to stack closer together
  \cite{wang_development_2004}. It is also possible that the tails prevent
  close stacking of monomer head groups and we do not achieve the timescales
  necessary for them to rearrange into a necessarily more tightly packed
  configuration. To test this chain-packing hypotheses, we equilibrated the
  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
  into a more tightly packed configuration. Before annealing and in order to
  stabilize the hexagonal phase at 500 K, we placed harmonic restraints with
  force constants of 1000 kJ mol$^{-1}$ nm$^{-2}$ between head group COMs within
  each column as well as between head group COMs in adjacent columns. We saw no
  improvement in packing distance over our 300 K models (see further discussion
  in Section~\ref{section:slow_dynamics}).

  %BJC: could move the following paragraph to supporting
  The system size, in the $z$-direction, does not significantly alter $g(z)$.
  In Figure~\ref{S-fig:correlation}, oscillations do not fully decay, so a taller
  system may be necessary to fully capture the correlation function. We therefore
  equilibrated a sandwiched system with twice as many monomers per column so that
  the system size doubled in the $z$-direction. The correlation length increases
  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
  correlation functions are nearly identical and oscillatory behavior persists
  throughout $g(z)$ in both cases (See
  Figure \ref{S-fig:z_correlation_overlay}).

@@

  % Moved to supporting info
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \centering
%  \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
%  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
%  \end{subfigure}  
%  \begin{subfigure}{0.45\textwidth}
%  \centering
%  \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
%  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
%  \end{subfigure}  
%  \begin{subfigure}{0.45\textwidth}
%  \centering
%  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
%  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
%  \end{subfigure}  
%  \begin{subfigure}{0.45\textwidth}
%  \centering
%  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
%  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
%  \end{subfigure}  
%  \caption{1D correlation functions of the center of masses of aromatic head
%	  groups, $g(z)$, show decaying oscillatory behavior and have consistent
%	  correlation lengths with experiment. We calculated the correlation length by
%	  fitting a decaying exponential function
%	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
%	  correlation length is longer for ordered basin systems
%	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
%	  correlation length for (d) because there are no clear peaks. We assume that
%	  this correlation length is less than the vertical distance between
%	  monomers.}\label{fig:correlation}
%  \end{figure}

@@

  An exact quantitative comparison between the intensity and FWHM of the
  experimental and simulated cross-sections of R-$\pi$ is not feasible for
  several reasons. Experimental peaks broaden due to effects that we can not
  easily simulate such as finite size crystalline domains and instrumental
  resolution~\cite{girolami_x-ray_2016}. In our simulated XRD patterns, 
  the system size imposes limitations
  on the resolution, which makes it difficult to reliably fit peaks. This is
  especially problematic when comparing the FWHM of the $q_z$ cross-section of
  R-$\pi$, where the experimental FWHM (0.11 $\AA^{-1}$) is similar to the bin
  size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).  Additionally, we model each
  atom with a Gaussian sphere of electron density, which is a simplification.
  However, we can explore reasons for which differences in the simulation
  structure could change the peak shapes and intensities to be in better
  agreement with experiment.

@@

%  Increasing thermal noise in the $z$-direction will reduce the intensity
%  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increased the
%  thermal noise of the simplified parallel displaced system in the $z$-direction by
%  12\% and 27\%, we saw a 3 and 15-fold decrease in the maximum intensity of 
%  R-$\pi$ respectively (Figure~\ref{fig:intensity_vs_zsigma}). Despite the decrease in 
%  intensity, the 3 cross-sections have the same shape 
%  (Figure~\ref{fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
%  not consistent with experiment. 
%  
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.49\textwidth}
%  \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
%  \caption{}\label{fig:intensity_vs_zsigma}
%  \end{subfigure}
%  \begin{subfigure}{0.49\textwidth}
%  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
%  \caption{}\label{fig:rpi_xsection_vs_zsigma}
%  \end{subfigure}
%  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
%  thermal noise in the $z$-direction; however, the $q_r$ cross-section profile does
%  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
%  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
%  background intensity, relative to systems with simulation levels of disorder (blue)
%  by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor 
%  of 15 when we increase $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
%  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
%  \end{figure}

  When we allow simplified monomer columns to move independently in the
  $z$-direction, the intensity of R-$\pi$ drops and the $q_r$ cross-section of
  the simulated diffraction patterns smooths out. We can demonstrate this by
  creating a simplified sandwiched configuration (as described above), with
  varying amounts of statistical correlation between columns (see
  Figure~\ref{fig:column_displacement}). In the low independent motion limit, the
  COM of columns are situated at the same $z$-coordinate.  We allow increasing
  independence of columns by randomly shifting each column in the $z$-direction
  according to a uniform distribution bounded by (0, $f \times \mathit{d}$) where
  $f$ ranges between 0 and 1 and $d$ is the vertical distance between scatterers.
  When $f = 1$, the columns move independently and the $q_r$ cross-section
  smooths out completely (Figure~\ref{fig:sf_qy_sr100}). Any amount of dependence
  results in some presence of sharp peaks, though significantly attenuated at $f$
  nearer 1. The intensity of R-$\pi$ also decreases with increasing column
  independence. We see an 9-fold decrease in the intensity of R-$\pi$ when $f=1$
  versus when $f=0$ for our simplified model systems.

@@

  %BJC: I could move the following paragraph to supporting information since it
  % relies on a qualitative comparison between the following figure and the 
  % the original correlation functions which I moved to supporting already.
  It therefore seems likely that the discrepancy between the shape and intensity of
  R-$\pi$ generated from our simulations versus experiment is primarily due to
  highly correlated columns in our highly symmetric initial configurations.
  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
  would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
  average all $z$-slices of the 3D correlation function. Contributions to
  $g(z)$ from head groups in other columns within the same pore, and with head
  groups in different pores would cancel out. However, when we include all 
  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
  $z$-slices within 2.1~\AA~of the center of the correlation function 
  (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
  behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
  reinforced by head groups in neighboring columns which is not expected
  in a system where columns act independently.

@@

  We also used our simplified systems in order to study the influence of increased
  disorder in each dimension. Increasing $z$-directional disorder reduces the
  intensity of R-$\pi$ without changing the shape of its $q_r$ cross-section.
  Increasing disorder on the $xy$ plane, somewhat counterintuitively, reduces
  the FWHM of the $q_r$ cross-section of R-$\pi$ with an insignificant effect
  on its intensity. We explain these points in more depth in 
  Section~\ref{S-section:simplified_sf}.

%  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
%  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a
%  system with uncorrelated columns, we modified the disorder in both the $r$ and
%  $\theta$ directions by multiplying their values by a factor of 0.5 and 2
%  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
%  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
%  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
%  with experiment, meaning the quenched configuration contains about the right
%  amount of disorder on the $xy$ plane. However, the relatively low quality of
%  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
%  simulation might not be the best comparison to experiment and that some form of
%  initial configuration dependence causes extra structure.
%
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
%  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
%	  FWHM of the $q_r$ cross-section of R-$\pi$. When we cut the amount of $r$ and
%	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
%	  we double the disorder (Noise factor = 2), the FWHM decreases by
%	  51\%.}\label{fig:qy_fwhm}
%  \end{figure}

@@

  The ether dihedrals become decorrelated on a reasonable timescale when we raise
  the system temperature. At 300 K (Figure~\ref{S-fig:dihedrals_300K}), the autocorrelation function does
  not cross the $x$-axis until $\sim$105 ns meaning that tails fully rotate on average about 
  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
  function plateau's near a value of -0.2 which indicates that the tails are starting in 
  an unfavorable configuration. We implemented distance restraints between the centers of 
  mass of monomer head groups to preserve the hexagonal phase, then raised the temperature 
  of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
  decorrelation of the ether dihedrals after $\sim$11 ns with a plateau at 0, 
  (Figure~\ref{S-fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
  the resultant configuration back down to 300 K over 200 ns to see if the increased rotational
  freedom might allow the system to relax into to a more tightly packed configuration.

@@

  %BJC: moved to SI
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.pdf}
%  	\caption{300K}\label{fig:dihedrals_300K}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  	\centering
%  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.pdf} % Run : torsions.py -t tethered_columns.xtc -g tethered_columns.gro (the appropriate dihedral is the default)
%  	\caption{500K}\label{fig:dihedrals_500K}
%  \end{subfigure}
%  \caption{The outer tail ether dihedrals become decorrelated on a reasonable
%  timescale when we raise the system temperature. (a) The dihedrals do not
%  become decorrelated for ca. 100 ns when the system is equilibrated at 300 K.
%  (b) The ether dihedrals become decorrelated after 11 ns when the temperature
%  of the system is increased to 500 K.}\label{fig:dihedrals}
%  \end{figure}
